Neural Textures make Better Simulators ``I can't believe it's not real!"

### 2022-06-11 CORL/example.tex
Created appendix; Moved figure to appendix
Wrote unprojection consistency loss section

@@

\title{TRITON: Globally Consistent Sim-to-Real Transfer

@@

@@

In total, the loss for the image translator module $T$ is $\ell_T=\ell_{cyc}+\ell_{rec}+\ell_{con}+\ell_{adv}$

@@

\subsection{Unprojection Consistency Loss}

@@

Heres the equation for unprojection consistency loss:
$\ell_{UC} = \mu\left(\sigma\left(u\right)_{1 \dots L}\right)$

This benefits from large batch sizes, but that often makes you run out of vram.

Also, you have to get lucky - two scene pictures have to show the same side of a cube for example. First person scenarios would be even worse.

Also, the resolution of the unprojection matters:

@@

>>>>

%TODO:
%	Formulation Section
%	Figures
%		Main diagram - break it up into pieces with just text
%		UVL three-axis diagram
%		Replace C with (pi,s)
%	Method:
%		Unprojection Consistency Loss
%		Texture Reality Loss

%TODO:
%	Formulation Section
%	Figures: Main diagram - break it up into pieces with just text
%	Figures: UVL three-axis diagram
%	Method:	Unprojection Consistency Loss
%	Method:	Texture Reality Loss

\newcommand{\toB}{_{1\dots B}}
\newcommand{\toBL}{_{1\dots B,1\dots L}}
\newcommand{\toL}{_{1\dots L}}

\newcommand{\lUC}{\ell_{UC}}
\newcommand{\lTR}{\ell_{TR}}

@@

% \title{TRITON: Globally Consistent Sim-to-Real Transfer
\title{Neural Textures make Better Simulators

@@

	QUESTIONS FOR MICHAEL:
	\begin{itemize}
		\item - TODO: WE MAINTAIN WHAT WE NOW CALL "SURFACE CONSISTENCY" instead of view consistency! Or texture consistency? Etc? What should we call it?
	\end{itemize}

@@

In total, the loss for the image translator module $T$ is $\ell_T=\ell_{cyc}+\ell_{rec}+\ell_{con}+\ell_{adv}$.

@@

\subsection{Unprojection Consistency Loss}
\label{unprojection_consistency_loss}

@@

To maintain surface consistency, we sample a random batch of UVL scenes $S\toB$, and translate them into $\ph\toB$.
Using geometric knowledge of the scene encoded in $S\toB$, we individually unproject each $\ph_i \in \ph\toB$ back into texture space, to obtain $B$ sets of $L$ unprojected textures $u\toBL$.
We then use the per-pixel, batch-wise standard deviation of the unprojections as unprojection consistency loss $\lUC = \sigma(u\toBL)\toL$.
This loss observes how badly these unprojections differ from one another, and thus how different the object surfaces appear between translations.

Intuitively, if $\lUC$ were $0$, it would mean the object surfaces in translations $\ph$ appear exactly the same in every scene.

This loss is a fairly intuitive and effective way to maintain surface consistency. There are some caveats to this loss, however.
In order to produce a standard deviation greater than $0$, we must have a batch size greater than $1$.
In fact, $\lUC$ is most useful with large batch sizes because observing the same surface in multiple elements of a batch becomes more likely as the batch size increases.
There is a limited number of elements we can fit into video memory, so environments that rarely show a particular region of a surface will rarely have $\lUC$ applied to that region.
In first-person environments, this might be more of a problem - particularly when exploring multiple rooms (a task we haven't done though - should I mention this?)

To michael: Should we mention these caveats in this section, or mention them in the texture realism loss section? That section addresses all of these issues...

% Also, you have to get lucky - two scene pictures have to show the same side of a cube for example. First person scenarios would be even worse.

@@

\section{Appendix} 
Also, the resolution of the unprojection matters:
